Designing and Developing a Personalised Recommender System

### 2021-02-07 paper/paper.tex
tried using SVD on all reviews, didn't work
about to add item-based CF

\subsection{Data preparation and feature selection}
Prepare data
Of the 209,393 businesses in the dataset, 168,903 are still open. 
There are 43,980 restaurants which are open and contain 'Restaurant' as one of the categories. 
502 businesses in the overall dataset don't list anything in their categories section. 
43,052 businesses had at least 1 check-in. 
There are 4,223,201 reviews of restaurants. 
695,951 tips for these restaurants. 
1,968,703 users. 
43,992 restaurants listed with covid features, 8 restaurants which make up 12 duplicate entries 
(8 have 2 entries and 4 have 3 entries), the only difference between their entries being in the 
"Virtual Services Offered" section. 
Allow to pick user ID of 10 users with most reviews made, to avoid cold start problem
4 users have over 10,000 reviews, the most is 14,455 (Victor, 8k3aO-mPeyhbR5HUucA5aA). 
I actually want to select the most reviews of the places I am accepting, restaurants. 
When taking the most reviews of restaurants in teh dataset, a threshold of 600 reviews gives a list of 10 users, 
with the most being 1747. 
I then checked each of these for how many different restaurants they had reviewed and the greatest number of times 
they had reviewed a single restaurant to check that none of them were just users who reviewed a small number of 
restaurants a huge amount of times each. 
All 10 users passed this criteria, with even the least active user having reviewed 496 unique restaurants, which will 
certainly avoid any cold-start problems. 
The entire Yelp dataset is huge and much of it is not necessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.

@@

\subsection{Recommendation techniques/algorithms}
The first recommender system is collaborative filtering.
I am using a weighted mixed combination of these two systems in order to produce the results
of my hybrid recommender system.

>>>>

\subsection{Data preparation and feature selection}
Prepare data
Of the 209,393 businesses in the dataset, 168,903 are still open. 
There are 43,980 restaurants which are open and contain 'Restaurant' as one of the categories. 
502 businesses in the overall dataset don't list anything in their categories section. 
43,052 businesses had at least 1 check-in. 
There are 4,223,201 reviews of restaurants. 
695,951 tips for these restaurants. 
1,968,703 users. 
43,992 restaurants listed with covid features, 8 restaurants which make up 12 duplicate entries 
(8 have 2 entries and 4 have 3 entries), the only difference between their entries being in the 
"Virtual Services Offered" section. 
Allow to pick user ID of 10 users with most reviews made, to avoid cold start problem
4 users have over 10,000 reviews, the most is 14,455 (Victor, 8k3aO-mPeyhbR5HUucA5aA). 
I actually want to select the most reviews of the places I am accepting, restaurants. 
When taking the most reviews of restaurants in teh dataset, a threshold of 600 reviews gives a list of 10 users, 
with the most being 1747. 
I then checked each of these for how many different restaurants they had reviewed and the greatest number of times 
they had reviewed a single restaurant to check that none of them were just users who reviewed a small number of 
restaurants a huge amount of times each. 
All 10 users passed this criteria, with even the least active user having reviewed 496 unique restaurants, which will 
certainly avoid any cold-start problems. 
I split the businesses into 10 groups, by the city which they are closest to, I did this by using latitude and 
longitude rather than State or City since this does not give actual distance and restaurants close to a border 
could then be mis-categorised. 
The entire Yelp dataset is huge and much of it is not necessary for my domain of bars.
As such I prepared the data by eliminating any data not relevant to my domain.
I selected features such as user ratings and a particular user's average rating,
since if a user typically rates places they go highly, but rates a particular bar low,
this is more significant than a user who always rates places low.

@@

\subsection{Recommendation techniques/algorithms}
The first recommender system is collaborative filtering.
I am using item-based collaborative filtering, since the number of users is larger than the number of items 
(1,968,703 users vs 209,393 businesses in the entire dataset), this gives greater accuracy of predictions. 
In this case the list of available items does not change, so a user-based method would be unnecessary. 
One of the requirements for this system is justifiability, and item-based methods make it much easier to 
explain why certain predictions were made. 
I am using a weighted mixed combination of these two systems in order to produce the results
of my hybrid recommender system.
